Comparison of Learning Outcomes for Simulation-Based and Traditional Curricula for Statistical Inference in a Designed Educational Experiment

### 2015-05-25 DefenseSlides/DepartmentalSeminar/JobsTalk.Rnw
Rename files, change data read-in path from dropbox, and cut a few jobs talk slides at the beginning

## Load Data
setwd("C:\\Users\\Karsten\\Dropbox\\Dissertation\\CurriculumStudy\\DraftTISE")
dat <- read.csv("./Data/DataForStudyAnalysis.csv",header=T)
#change factor level order to put sweeney as default control group
dat$room <- factor(dat$room.x, levels=c("sweeney", "kildee"))
dat$lab5perc <- dat$lab5perc * 100
dat$hw2perc <- dat$hw2perc * 100
dat$treatment <- "Simulation-Based"
dat$treatment[which(dat$room=="sweeney")] <- "Traditional"
@

@@

\title[Comparison of Learning Outcomes for Simulation-Based and Traditional Curricula for Statistical Inference in a Designed Educational Experiment]{Comparison of Learning Outcomes for Simulation-Based and Traditional Curricula for Statistical Inference in a Designed Educational Experiment}
\author[K. Maurer]{Karsten Maurer}
\date{February 2, 2015}
\institute[ISU]{Iowa State University}
\begin{document}

@@

\begin{frame}
    \frametitle{Educational Background}

    \begin{itemize}
        \item BA in Statistics and History from University of Minnesota, Morris (2009)
        \item MS in Statistics from Iowa State University (2011)
        \item PhD in Statistics In Progress at Iowa State University (Planned Summer 2015)
    \end{itemize}

\begin{frame}
    \frametitle{Research Interests}
Statistics Education
        \begin{itemize}
          \item Technology for Stat Ed
          \item Curriculum Development
        \end{itemize}

Statistical Graphics
        \begin{itemize}
          \item Visualization of Large Data Sources
          \item Graphical Perception
        \end{itemize}

>>>>

## Load Data
# setwd("C:\\Users\\Karsten\\Dropbox\\Dissertation\\CurriculumStudy\\DraftTISE")
dat <- read.csv("DataForStudyAnalysis.csv",header=T)
#change factor level order to put sweeney as default control group
dat$room <- factor(dat$room.x, levels=c("sweeney", "kildee"))
dat$lab5perc <- dat$lab5perc * 100
dat$hw2perc <- dat$hw2perc * 100
dat$treatment <- "Simulation-Based"
dat$treatment[which(dat$room=="sweeney")] <- "Traditional"
@

@@

\title[Comparison of Learning Outcomes for Simulation-Based and Traditional Curricula for Statistical Inference in a Designed Educational Experiment]{Comparison of Learning Outcomes for Simulation-Based and Traditional Curricula for Statistical Inference in a Designed Educational Experiment}
\author[K. Maurer]{Karsten Maurer}
\date{June 4, 2015}
\institute[ISU]{Iowa State University}
\begin{document}

@@

% 
% \begin{frame}
%     \frametitle{Educational Background}
% 
%     \begin{itemize}
%         \item BA in Statistics and History from University of Minnesota, Morris (2009)
%         \item MS in Statistics from Iowa State University (2011)
%         \item PhD in Statistics In Progress at Iowa State University (Planned Summer 2015)
%     \end{itemize}
% 
% \end{frame}

% %--------------------------------------------------------------
% 
% \begin{frame}
%     \frametitle{Research Interests}
% Statistics Education
%         \begin{itemize}
%           \item Technology for Stat Ed
%           \item Curriculum Development
%         \end{itemize}
%         
% Statistical Graphics
%         \begin{itemize}
%           \item Visualization of Large Data Sources
%           \item Graphical Perception
%         \end{itemize}
% 
% \end{frame}
